---
title: "Quiz03"
author: "Maria C. Codlin"
date: "October 31, 2017"
output: html_document
---
I couldn't find my last quiz in the repository. I certainly did it though! I put it back in there. Did it miss grading? Nevermind, it wasnt the right one. Oh it was in quiz one...
```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

```{r}
library(dplyr)
survivor<- d%>%filter (major=="medicine/nursing")%>%
  print
```
```{r}
m <- lm(data = d, years_of_education ~ age)
summary (m)
```

The linear model shows that for nursing/med majors, there is a small .3% positive relationship between age and years of education and that this is significant at 95% confidence level. But this effect seems very small and not likely a very useful relationship.

```{r}
library (ggplot2)
d$gender<- as.factor(d$gender)
g <- ggplot(data = d, aes(x = age, y = years_of_education))
g <- g + geom_point(aes(color=factor(gender)))
g <- g + scale_color_manual(values=c("blue", "pink")) #not sure why this removes the legend
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g
```


